---
title: "STAT184HW5"
author: "Marc Hughes"
output: html_notebook
---


```{r}
#load in Minneapolis2013 data 
install.packages("devtools")
library(devtools)
install_github("mdbeckman/dcData")
library(dcData)
data("Minneapolis2013", package = "dcData")
library(tidyverse)
```


# Exercise 7.3

1.) 
```{r}
Minneapolis2013 %>%
  summarise(count = n())
```

There are 80,101 cases

2.) 
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

The top 5 candidates were; Betsy Hodges, Don Samuels, Mark Andrew, Jackie Cherryhomes, and Bob Fine

3.)

```{r}
Minneapolis2013 %>%
  summarise("Undervotes in First" = sum(First == "undervote"),
            "Undervotes in Second" = sum(Second == "undervote"),
            "Undervotes in Third" = sum(Third == "undervote"))
```

Undervotes in first choice selections: 834
Undervotes in second choice selections: 10598
Undervotes in third choice selections: 19210

4.)

```{r}
Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

The top 3 combinations of first and second vote selections were; Betsy Hodges and Mark Andrew, Betsy Hodges and Don Samuels, and Mark Andrew and Betsy Hodges respectively.

5.)

```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

Precinct "P-06" had the highest number of ballots cast.

# Exercise 7.5

a)

```{r}
VoterData_A <-
  Minneapolis2013 %>%
  group_by(First, Second)
```

VoterData_A has been modified by grouping by the "First" and "Second" variables. This does not actually change what a case represents in the data set, so the case of VoterData_A is still voters' choices on a rank-choice election ballot.

b) 

```{r}
VoterData_B <-
  Minneapolis2013 %>%
  summarise( total = n() )
```

VoterData_B has been modified by using the summarise() function to find the total number of cases in the "Minneapolis2013" data set. In the VoterData_B data set a case simply represents the total number of ballots cast.

c)

```{r}
VoterData_C <-
  Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise( total = n() )
```

VoterData_C has been modified by using the group_by() and summarise() function to find the total number of combinations between the first and second vote selections in the ballots.

d)

```{r}
VoterData_D <-
  Minneapolis2013 %>%
  summarise( total = n() ) %>%
  group_by(First, Second) 
```

The variable "First is now unknown because the code executes the line with the summarise() function prior to the group_by() function. As a result, the data set is modified to count the total number of cases and display the variable "total". There is no longer any columns matching the names "First" or "Second", so the code results in an error.

# Exercise 7.7

a.) There will be the following three variables; "sex", "count", and "meanAge".

b.) There will once again be three variables; "diagnosis", "count", and "meanAge".

c.) There will be the following four variables; "sex", "diagnosis", "count", and "meanAge".

d.) There will be the following four variables; "age", "diagnosis", "count", and "meanAge".

e.) There will be the following three variables; "age", "count", and "meanAge".


