---
title: "STAT184HW5"
author: "Marc Hughes"
output: html_notebook
---


```{r}
#load in Minneapolis2013 data 
install.packages("devtools")
library(devtools)
install_github("mdbeckman/dcData")
library(dcData)
data("Minneapolis2013", package = "dcData")
library(tidyverse)
```


# Exercise 7.3

1.) 
```{r}
Minneapolis2013 %>%
  summarise(count = n())
```

There are 80,101 cases

2.) 
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

The top 5 candidates were; Betsy Hodges, Don Samuels, Mark Andrew, Jackie Cherryhomes, and Bob Fine

3.)

```{r}
Minneapolis2013 %>%
  summarise("Undervotes in First" = sum(First == "undervote"),
            "Undervotes in Second" = sum(Second == "undervote"),
            "Undervotes in Third" = sum(Third == "undervote"))
```

Undervotes in first choice selections: 834
Undervotes in second choice selections: 10598
Undervotes in third choice selections: 19210

4.)

```{r}
Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

The top 3 combinations of first and second vote selections were; Betsy Hodges and Mark Andrew, Betsy Hodges and Don Samuels, and Mark Andrew and Betsy Hodges respectively.

5.)

```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

Precinct "P-06" had the highest number of ballots cast.

# Exercise 7.5

a)

```{r}
VoterData_A <-
  Minneapolis2013 %>%
  group_by(First, Second)
```

VoterData_A has been modified by grouping by the "First" and "Second" variables. This does not actually change what a case represents in the data set, so the case of VoterData_A is still voters' choices on a rank-choice election ballot.

b) 

```{r}
VoterData_B <-
  Minneapolis2013 %>%
  summarise( total = n() )
```

VoterData_B has been modified by using the summarise function to find the total number of cases in the "Minneapolis2013" data set. In the VoterData_B data set a case simply represents the total number of ballots cast.

c)

```{r}
VoterData_C <-
  Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise( total = n() )
```



